---
title: "Iceland Archaeology: Bibliometrics"
author: "Robert Z. Selden, Jr."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
bibliography: book.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bibliometrics

The dataset used in this analysis was harvested from [Scopus](https://www.elsevier.com/solutions/scopus), includes all articles published containing _iceland_ AND _archaeology_ in the title, abtract, or keywords, and was analysed using the `bibliometrix` package [@RN20997].

```{r bibliometrix, echo=TRUE, warning=FALSE}
# install bibliometrix and load data
# devtools::install_github("massimoaria/bibliometrix")

library(here)
library(bibliometrix)
library(reshape2)
library(ggplot2)
df <- convert2df(file = "arch.bib", 
                 dbsource = "scopus", 
                 format = "bibtex")
```

## Descriptive analysis

```{r summary, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
results <- biblioAnalysis(df, 
                          sep = ";")
options(width = 100)
s <- summary(object = results, 
             k = 20, 
             pause = FALSE)

# plot attributes
plot(x = results, 
     k = 20, 
     pause = FALSE)
```

### Attributes of the local network

```{r local.attr, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# calculate citations in local network
CR <- localCitations(df, sep = ";")

# top 20 cited authors in local network
CR$Authors[1:20,]

# top 20 cited papers in local network
CR$Papers[1:20,]
```

## Most cited

### Most cited articles

```{r most.cited.refs, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# most cited references in global network
mcr <- citations(df, 
                 field = "article", 
                 sep = ";")
cbind(mcr$Cited[1:20])
```

### Most cited authors

```{r most.cited.auths, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# most cited authors in global network
mcr <- citations(df, 
                 field = "author", 
                 sep = ";")
cbind(mcr$Cited[1:20])
```

### Author dominance ranking

```{r auth.dom, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
dom <- biblioAnalysis(df)
dom.r <- dominance(dom)
dom.r
```

## Intellectual structure

### Author co-citation

Co-citation analysis is the most commonly used bibliometric analysis method [@RN20999], and is defined as two publications that are cited together in one article [@RN21000].

```{r auth.co.cite, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# extract author names from reference items
df <- metaTagExtraction(df,
                        Field = "CR_AU")

# author co-citation network
auth.co.mat <- biblioNetwork(df, 
                             analysis = "co-citation", 
                             network = "authors", 
                             sep = ";")

# network plot
auth.co.net = networkPlot(auth.co.mat, 
                          n = 50, 
                          Title = "Author Co-Citation Network", 
                          type = "auto", 
                          size = 10, 
                          size.cex = T, 
                          remove.multiple = FALSE, 
                          labelsize = 0.5, 
                          edgesize = 8, 
                          edges.min = 3, 
                          remove.isolates = TRUE)

# descriptive analysis of author co-citation network
auth.co.netstat <- networkStat(auth.co.mat)
summary(auth.co.netstat, k = 15)
```

### Author coupling

Coupling is a similarity measure that uses citation analysis to illustrate a similarity relationship between documents. Author coupling occurs when two authors reference a common third author in their bibliographies.

```{r auth.coup, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# author coupling network
auth.coup.mat <- biblioNetwork(df, 
                             analysis = "coupling", 
                             network = "authors", 
                             sep = ";")

# network plot
auth.coup.net = networkPlot(auth.coup.mat, 
                          n = 50, 
                          Title = "Author Coupling Network", 
                          type = "mds", 
                          size = 25, 
                          size.cex = T,
                          remove.multiple = FALSE, 
                          labelsize = 0.5, 
                          edgesize = 10, 
                          edges.min = 8, 
                          remove.isolates = TRUE)

# descriptive analysis of author coupling network
auth.coup.netstat <- networkStat(auth.coup.mat)
summary(auth.coup.netstat, k = 15)
```

## Historiograph direct citation linkages

The historiographic map is a chronological network map of the most relevant direct citations resulting from this bibliographic collection.

```{r hdcn, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# historical citation network
options(width = 100)
histResults <- histNetwork(df, 
                           min.citations = 20, 
                           sep = ";")

# plot historical co-citation network
hnet <- histPlot(histResults, 
                 n = 100, 
                 size = 6, 
                 labelsize = 2)
```

### ID and DE keyword associations

```{r key.assoc, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
list <- keywordAssoc(df, 
                     sep = ";", 
                     n = 10)

list[[1]][1:10]
```

### Yearly occurrences of top keywords/terms

#### Authors' keywords

```{r key.growth, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
topKW = KeywordGrowth(df, 
                      Tag = "DE", 
                      sep = ";", 
                      top=10, 
                      cdf=TRUE)

topKW

# plot results
key.plot = melt(topKW, 
                id='Year')

ggplot(key.plot, aes(Year, 
                     value, 
                     group = variable, 
                     color = variable)) + 
  geom_line()
```

#### Publisher's keywords

```{r key.growth2, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
topKW = KeywordGrowth(df, 
                      Tag = "ID", 
                      sep = ";", 
                      top=10, 
                      cdf=TRUE)

topKW

# plot results
key.plot = melt(topKW, 
                id='Year')

ggplot(key.plot, aes(Year, 
                     value, 
                     group = variable, 
                     color = variable)) + 
  geom_line()
```

## Conceptual structure

### Co-word analysis

The co-word analysis maps the conceptual structure of a research domain using the co-occurrence of author keywords in the bibliographic collection.

#### Authors' keywords

```{r co.word, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# using authors keywords
cw <- conceptualStructure(df, 
                          field = "DE", 
                          method = "MDS", 
                          minDegree = 2, 
                          clust = "auto", 
                          stemming = FALSE, 
                          labelsize = 10, 
                          documents = 50)
```

#### Publisher's keywords

```{r co.word2, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# using publishers keywords
cw <- conceptualStructure(df, 
                          field = "ID", 
                          method = "MDS", 
                          minDegree = 2, 
                          clust = "auto", 
                          stemming = FALSE, 
                          labelsize = 5, 
                          documents = 50)
```

## Social structure

### Author collaboration 

Scientific collaborations are plotted where nodes are authors and links are co-authorships, illustrating collaborations between authors.

```{r auth.collab, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# author collaboration network
auth.collab <- biblioNetwork(df, 
                             analysis = "collaboration", 
                             network = "authors", 
                             sep = ";")

# network plot
auth.collabnet = networkPlot(auth.collab, 
                             n = 100, 
                             Title = "Author Collaboration", 
                             type = "mds", 
                             size = 20, 
                             size.cex = T,
                             edgesize = 2, 
                             labelsize = 0.5,
                             remove.multiple = TRUE,
                             remove.isolates = TRUE)

# descriptive analysis of author collaboration network
auth.collab.netstat <- networkStat(auth.collab)
summary(auth.collab.netstat, k = 15)
```

### Edu collaboration

Scientific collaborations are plotted where nodes are institutions and links are co-authorships, illustrating collaborations between institutions.

```{r edu.network, out.width = "100%", dpi = 300, echo=TRUE, warning=FALSE}
# author collaboration network
edu.collab <- biblioNetwork(df, 
                            analysis = "collaboration", 
                            network = "universities",
                            sep = ";")

# network plot
edu.collabnet = networkPlot(edu.collab, 
                            n = 100, 
                            Title = "Edu Collaboration", 
                            type = "auto", 
                            size = 30, 
                            size.cex = T, 
                            edgesize = 2, 
                            labelsize = 0.4, 
                            remove.isolates = TRUE)

# descriptive analysis of edu collaboration network
edu.collab.netstat<-networkStat(edu.collab)
summary(edu.collab.netstat, k = 15)
```

## Colophon

This version of the analysis was generated on `r Sys.time()` using the following computational environment and dependencies: 

```{r colophon, cache = FALSE}
# what R packages and versions were used?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

Current Git commit details are:

```{r}
# where can I find this commit? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

## References cited
